%%=====================================================================================
%%
%%       Filename:  modernsgeneral.tex
%%
%%    Description:  
%%
%%        Version:  1.0
%%        Created:  01/27/2015
%%       Revision:  none
%%
%%         Author:  YOUR NAME (), 
%%   Organization:  
%%      Copyright:  
%%
%%          Notes:  
%%                
%%=====================================================================================

\documentclass[10pt]{article}
\begin{document}
\section{Marks of the Era}
\begin{itemize}
	\item Many new things happen in the ``modern'' era.  Faced with a 
		world war followed by deep economic instability, there comes a 
		cynical view and a question as to whether ideals can survive 
		catastrophe.
	\item People begin to examine human behavior through psychology.
	\item ``Modernism,'' for lack of a better definition, was a term for 
		the new, bold, experimental styles and forms that swept 
		through the arts throughout the first part of the 20th century.
\end{itemize}

\section{Historical Events}
\begin{itemize}
	\item 1901, Queen Victoria dies
	\item 1905, Theory of Relativity proposed
	\item 1909, Freud lectures on psychoanalysis
	\item 1914, WW1
	\item 1932, FDR
	\item 1941, Bombing of Pearl Harbor
	\item 1944, June 6th, D-Day
\end{itemize}

\section{Events in Literature}
\begin{itemize}
	\item The concept of the ``American Dream,'' an interesting falsehood, 
		is comprised of the admiration of America as a land of beauty, 
		bounty, and unlimited promise, optimism, and the idea of 
		self-reliance and the individual.
	\item WW1 was a very influential force on writers in the early 20th 
		Century.  Hemingway writes \underline{A Farewell to Arms}
	\item The Jazz Age also happens here.  People looked for an escape in 
		the pleasures of entertainment and good times.  The Roaring 
		Twenties, with its booming economy, results.
	\item Womens' lives changed in the twenties, and flappers happened.  
		Flappers were cool.
	\item Prohibition happens, Then the depression happens.
	\item Psychoanalysis and Marxism have an effect on literature.  Freud 
		and stuff.  As a result of these two forces, literature finds 
		stream-of-consciousness writing.
	\item The Octopus, by Frank Norris.  The Souls of Black Folk by W.E.B. 
		Dubois, a collection of poems by William Carlos Williams, and 
		O Pioneers! by Willa Cather.  Main Street, by Sinclair Lewis.  
		The Waste Land by T.S. Eliot.  The Great Gatsby.
	\item The Weary Blues, Sam Spade, and Their Eyes were Watching God by 
		Zora Neale Hurston.  Our Town, a play.  Native Son, a novel.  
		The Glass Menagerie, another playwright.  1949 Arthur Miller 
		writes Death of a Salesman.  2014, Jacob Erney stars in the 
		Little Theatre's performance, which was a stressful play but 
		turned out decently.
	\item The \bf{Harlem Rennaisance} takes place, and African-american 
		culture finds expression in poetry in two ways: Conventional 
		poetry (Dunbar) and poetry focusing more on the unique 
		contributions of African-American culture to America (Hughes, 
		Cullen)
\end{itemize}
\end{document}
