\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[light]{merriweather} %% Option 'black' gives heavier bold face

\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\begin{document}
\section{Page 183 Catholic Life in Action #1 & #2}
\begin{enumerate}
	\item The Checklist:
		\begin{enumerate}
			\item \xmark
			\item \xmark
			\item \xmark
			\item \xmark
			\item \xmark
			\item \xmark
			\item \xmark
			\item \xmark
			\item \xmark
			\item \xmark
		\end{enumerate}
		Alternately, all checks.  I don't have feelings on whether these things are
		keeping me from Jesus, as my main objections are with the concept of the 
		Christian theology rather than things holding me back from faith.
	\item A haiku:
		\begin{center}
			love is that which those \\
			who find themselves in it \\
			find it is to them
		\end{center}
\end{enumerate}

\section{Page 197 A Family of Humanity}
\begin{enumerate}
	\item Generally speaking, America as a whole have trouble with Muslim people,
		especially those of middle-eastern descent.  Racism against black people is
		also still a strong thing in America, if a bit better hidden than it used
		to be.  In my school, viewpoints on those who are not Catholic are better
		than expected (though of course there still is a bit of prejudice) but the
		viewpoint of people with sexualities outside heterosexuality (homosexuality,
		bisexuality, pansexuality, asexuality, etc.) tends to be more negative than
		it ought.
	\item Technically, of course I've been discriminated against.  I would not say
		that as a white man from an upper-middle class background, however, that I
		have faced anywhere near as much discrimination as many others, especially 
		in that I come from a non-judgemental family and have decent people for 
		friends.
	\item Laws cannot do much on their own.  In order to change opinions, there
		must be a shift in culture around those with prejudice.  This can be seen
		very well in the improvements of our society's view on gay rights.
		Specifically, gay marriage.  That is, marriage as defined legally, in the 
		context that ``Congress shall make no law respecting an establishment of 
		religion,'' and not sacramental marriage which has no influence on over
		half of all americans anyway (assuming that only the Catholic Church can 
		administer ``true'' marriage.
	\item I call people on things like that.  When ``gay'' is thrown as an insult,
		I make a point of it to speak up.  When racist slurs are spoken, I try not
		to let it slide.
\end{enumerate}

\section{Page 201 Peace Begins With Me}
\begin{enumerate}
	\item Aggression among teens leading to school shootings comes from very 
		unwell individuals hurt deeply by the society they proceed to slaughter.
		The behavior is inexcusable, but it also comes from a place of very unsound
		thought.  Those willing to shoot up a school are probably insane in some
		form, if for nothing other than how poor a decision it is.
	\item Perhaps a reform of the school system to help people not feel like they
		are drowning if they make a mistake.  Perhaps a reform of school policy so
		that teachers can afford the energy to care about the individual student.  
		Perhaps a means to prevent bullying.  The system in its current form is 
		horribly broken and I have a lot more I could say but I need to finish this
		sometime tonight.
\end{enumerate}

\section{Page 217 Sex Attitudes}
Preface: This will be fun.
\begin{enumerate}
	\item 5 --- Depends heavily on the individual, far more so than based on the
		gender (or, for that matter, biological sex) of the person.
	\item 4 --- In its current form, the porn industry is pretty messed up, and
		supporting it is not really morally sound.  This does not mean that the 
		viewing of *any* pornography is immoral, just the support of the industry
		that produces commercial porn is not an easy thing to defend in my eyes.
	\item 5 --- Sex is meant for two individuals who consent and whatever purpose
		they feel it serves.  I am not much of one to decide another's life for
		them.
	\item 2 --- Humans are sex-obsessed in general, and our society has the
		interesting bonus of using sex as marketing.  Adding to the obsession with 
		sex is our bizarre view of the human body as inherently powerfully sexual
		and even wrong to be seen.
	\item ? --- I know for a fact my definition of responsible is different from
		that of the church, but going by my definition absolutely.  It's not even
		difficult, you just have to know what you're doing and be a little careful.
	\item 1 --- Isn't it obvious?
	\item 3 --- It is absolutely acceptable and the couple does not have to be 
		in love.  All that is required for it to be reasonable is communication
		between the partners.
	\item 1 --- I could rant for a solid half hour on double standards and if you
		would like to hear I can come in after class some day.  It's a topic I feel 
		strongly about.
	\item 4 --- ``Prepare for marriage?'' What even does that mean with regards 
		to chastity?  If you can't get married to someone because they had 
		sex---even a lot of sex---in high school or college, and they test negative,
		then you have some serious issues going on independent of them.
	\item 5 --- The fact that there will be men who answer 1, 2, or 3 on this,
		hell, that it even has to be included, makes me furious about the state of
		our society.
	\item 5 --- Sex ed has been \underline{proven} to decrease STI transmission 
		and teen pregnancy dramatically as compared to abstinence-only or no sex ed
		at all.  Teens will still have sex if you don't teach them about condoms, 
		they will just be having unprotected sex instead.
	\item 5 --- See above questions.  Sex can mean something outside of marriage, 
		between two people of the same gender, just the same as it can inside a
		marriage.
	\item 1 --- I don't believe in the sacrament of marriage, I believe in the
		secular institution of marriage.  Which should allow gays the same rights
		as anyone else.
\end{enumerate}
\begin{itemize}
	\item Men are expected to have lots of sex and be straight if they want to be
		``Masculine.''  Women are expected to withhold sex or they are considered 
		``sluts.'' Who are the men supposed to be getting with, anyway?
	\item Literally half of all advertising, most big movies, much of TV, the
		list goes on.  This is demeaning to women because media is viewing them
		as good only for sex and not for all the other things people tend to be 
		good for.  Like science.  More girls in science, less in skimpy outfits.
		You have my campaign slogan.
	\item Men treat women with aggression and from a perspective of perceived 
		superiority from this macho image.  It's ridiculous.
\end{itemize}

\section{Page 222 A Case to Discuss: Changed Vows}
\begin{enumerate}
	\item I don't view civil marriage as permanent, only long-term, and I'm not
		exactly sacrament of marriage material.  I feel like the society implies
		the allowance of divorce by how it happens so often, but I don't really
		have a problem with this change.  It's just kind of unnecessary and I think
		it sounds a bit dumber.
	\item True unconditional love is a myth.  Functionally unconditional love is 
		the willingness to love another regardless of their actions.  It is the
		form of love given from parent to child in most parent child relationships.
	\item Ooh.
		\begin{itemize}
			\item Continue dating the person.
			\item Firstly, people's viewpoints on whether to have children change, and
				secondly I currently don't want a kid and never see myself wanting one,
				so I can sympathize.
		\end{itemize}
\end{enumerate}

\section{Page 239-240 What Is Your Honest Quotient?}
\begin{enumerate}
	\item 5
	\item 4
	\item 5
	\item 5
	\item 3
	\item N/A so 5
	\item 3
	\item 5
	\item 5
	\item 5
	\item 4
	\item 2
	\item 5
	\item 3
	\item 4
	\item 4
	\item 2
	\item 1
	\item 2
	\item 5
\end{enumerate}
Grand Total: 77.  Not the worst.
\begin{enumerate}
	\item People are very underhanded.  The stereotype is that it applies to girls
		but in high school (and in a different sense in society at large) most
		people will lie to your face and talk smack behind your back.  This is not
		a simple situation to fix, but in no small part it comes from corporate
		culture in the world at large.
	\item Technically, it would be wrong, but the ends (not ruining one's chance
		at college and thus at a good career and thus at not being impoverished for
		the rest of time) can be seen as justifying the means.  When you subject the
		individual to great worry over a subject for years, to expect perfectly
		honest behavior is unlikely.  It would, however, be lying.
	\item The lovely concept of constructive criticism.  Tell her what's good
		about the essay, and then hand her some edits to make it, you know, not the
		worst ever.
	\item Usually it's pretty simple.  Anyone I trust gets the whole truth, and 
		anyone I don't gets the portion of the truth I'm willing to tell them, but 
		it's not hard to avoid outright lying in most cases.
	\item HONESTY IS ALWAYS THE BEST POLICY--- ok fine.  Any of my good 
		friendships and especially any good relationship must be built on 
		communication and trust.  So all of those I suppose.
\end{enumerate}

\section{Page 253 The Epidemic of Cheating}
\begin{enumerate}
	\item Cheating is fairly prevalent at Watterson, though a significant portion 
		of my friends are the honor student types who wouldn't be caught dead
		cheating.  Interestingly enough, I think cheating was more rampant at St.
		Charles than it is at Watterson, but that makes sense considering the
		difference in workload.
	\item Zero for the class for the year or some similar thing.  I don't keep
		track of it, because to be honest I'm not worried about being caught doing 
		a thing I don't do.  It's theoretically enforcable, but it doesn't get 
		enforced much because it's so harsh and cheating is so common.
	\item Depends on the parents.  My parents certainly value honesty and 
		integrity, but I know of less strict parents.
	\item If this question is involving cheating via plagiarism, it's very easy to 
		deal with.  Just google a couple of consecutive sentences in quotes and 
		see if anything comes up.
	\item Don't think so.  People would cheat anyway.  They do now and I have the
		sneaking suspicion that without significant overhaul of the educational
		system they will keep doing so.
\end{enumerate}
\end{document}
