\documentclass[11pt]{article}
\usepackage{fullpage}
\begin{document}
\begin{itemize}
	\item Old Law is justice-oriented, leaning legalistic.  New Law 
		is love-oriented,	leaning spirit of the law.
	\item Jesus is the fulfillment of the law, bringing new meaning 
		to the letter	of the law.
	\item The Our Father is an intimate prayer (in its original 
		format.)
	\item Included in the Our Father is the needs of the individual,
		and	the forgiveness of sins as far as we forgive.
	\item Sanctifying Grace is grace that makes an individual holy.
	\item People cooperate with the many graces God gives people 
		to live upright, holy lives to merit the reward God has in 
		store	for them.
	\item The source of all merit is the love of Christ whose 
		sacrifice has won everything.
	\item Holiness requires self-denial and prayer.
	\item Discipleship is the mandate of baptized Christians to 
		follow Jesus in Priestly, Prophetic, and kingly missions.
	\item Contemplative vs. Apostolic orders.
	\item Consciousness is a practical judgement
\end{itemize}
\subsection{Passages}
\begin{itemize}
	\item Virtues are good habits, and virtues are
		good habits.  You know this, because we haven't
		covered anything new these past 800 years.
	\item `` You must always form and keep informing
		your conscience. ''
	\item SEER - Search out the fact, E, Execute the
		action, Review the action.
	\item Fortitude is the moral virtue of... Well, you know.
	\item Erroneous conscience cannot always be held responsible
		for thinking the way they do.
\end{itemize}
\subsection{Other things or whatever}
\begin{itemize}
	\item Sin is doing something wrong even though an individual
		knows it is wrong.
	\item object of an action
	\item circumstances of an action
	\item end of an action
	\item Sin has a ``Divine Dimension.''  Essentially, God cares.
	\item New, exciting ways of causing pain.  Also new ways of 
		actually hurting others in a distinctly %non-BDSM
		sinful way.
	\item Sin can be translated as missing the mark, rebellion, 
		or guilt in Hebrew.
	\item know the act of contrition
\end{itemize}
\end{document}
