\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[light]{merriweather} %% Option 'black' gives heavier bold face

\begin{document}
\title{Notes on Faulkner}
\author{John Markiewicz}
\date{8th May, 2015}
\maketitle
\section{Faulkner's background}
\begin{itemize}
	\item Born in 1897, his earliest efforts were in poetry but was known for his
		fiction.  Yoknapatawpha county was his fictional county.
	\item 2 collections of stories, a couple volumes of poetry, several of the
		greatest American novels.
		\begin{itemize}
			\item The Sound and the Fury
			\item As I Lay Dying
			\item The Unvanquished
		\end{itemize}
	\item Faulkner is a very difficult author, and writes with the following:
		\begin{itemize}
			\item Inconsistent punctuation
			\item Other things which I haven't gotten down
		\end{itemize}
	\item Was awarded the Pulitzer Prize and the Nobel Prize.
\end{itemize}

\section{A Rose for Emily}
\begin{itemize}
	\item Narrator represents the town, and is very inquisitive.  The narration is
		first person.
	\item Faulkner attempts to keep the reader from perceiving the relation of 
		seemingly isolated effects.  He wants the reader to sympathise with Emily.
	\item Emily portrayed as a victim through:
		\begin{itemize}
			\item Her father's treatment of her
			\item The insanity in her family
		\end{itemize}
	\item The small town Southern setting and the social conventions of it are 
		very important to the story.  During this time period, and prior to it,
		there was the respect for the ``Southern Lady'' Archetype.  The whole old
		style Southern womanhood type of thing.
	\item Added to the fact that Emily's family was highly respected, she demanded
		the respect of a Southern Lady
	\item This leads Emily to live in the past, eventually being alone in the 
		house	save for the servant.
	\item Town representatives force their way into her house, and she is
		described as small, fat, and bloated, dressed in black.
\end{itemize}
\end{document}
