% Created 2015-09-04 Fri 05:56
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\date{\today}
\title{beowulf}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.5.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle
\tableofcontents

\section{Section 1}
\label{sec-1}
\subsection{Opening}
\label{sec-1-1}
\subsubsection{The book opens with Scyld Shefing's funeral}
\label{sec-1-1-1}
People mourn his death, because he was a great king.

Scyld was a great king because he was good at leading in battle, he had
sons (which allowed the lineage to continue,) and he came up from
nothing.  He was obeyed, because he was feared (Machiavellian ideals
long before Machiavelli.)  He was especially feared by his enemies, but
by his followers as well.

He treated his followers fairly and rewarded them for their work.  He
distributed the treasure to the warriors after battles.

Being good enough at battle to be feared saves him lives and helps
establishing peace.  He used violence and war for the sake of peace.
With peace in his land, his people could prosper.  Their needs would
be met.

\uline{Scyld} is the benchmark for a good king, and these qualities are what
all other kings are compared to.

\subsubsection{Hrothgar builds a hall}
\label{sec-1-1-2}
This is a mead-hall, for drinking.  The men would come home, and they 
would come to the hall and drink mead.  It was a place of eating, and
drinking, partying, and where the unmarried male warriors slept.

Hrothgar wanted his mead hall to be the biggest and best building, to
let his men know that he thought they were the best.  Hrothgar was 
proud, but not arrogant.  Pride is justifiable.  The Anglo-saxons were
not huge fans of humility.

The people have a good time until the attack of Grendel.  

\subsubsection{Grendel attacks}
\label{sec-1-1-3}
Grendel is a demon, evil for the sake of evil, and has great bloodlust. 
A descendant of Cain, and he's angry that he wasn't invited.  He's been
excluded, and laughed at, and kills 30 men (daily.)

This has been going on for 12 years, but after the second night they 
started moving away from the mead hall.  This made Grendel successful
in destroying the community, but only at night and he could not touch
the throne.

A weirgild is a way of making reparations in the Anglo-Saxon way of 
doing things.  This was common within a tribe, and it was a way of 
making a reparation and stop the bloodshed.  In battle, this happened
to go to the winning tribe.  They offer one to Grendel, who refuses
the offer on account of his bloodlust.

Hrothgar doesn't fight Grendel because it would be foolish and bad
for his people.  \textbf{Despite his pride, he puts the sake of his people}
\textbf{first.}

\subsubsection{Enter Beowulf}
\label{sec-1-1-4}
Beowulf, like Grendel, has the strength of 30 men.  He has a reputation,
and comes to help.

Beowulf helps Hrothgar for two reasons:
\begin{itemize}
\item Credentials, to add to his reputation.  Glory.
(Notably, the Anglo-Saxons didn't have an afterlife.  To live on, 
 one must be remembered by the Scopes.)
\item Beowulf's father did something, and went to Hrothgar's kingdom.  
Since Hrothgar paid Beowulf's father's Weirgild, Beowulf feels a 
debt of honor.  Even though he doesn't technically owe Hrothgar a
thing, he wants to help.
\end{itemize}

The people of his clan read the omens and believe Beowulf will have fate
on his side.  The omens are good.

Beowulf knows it will be equal, and things are looking good.

\subsubsection{Beowulf arrives}
\label{sec-1-1-5}
Immediately Beowulf's group are dressed well and in warrior's clothing,
but are open about it.  Beowulf has the "Head of a Hero" meaning he has
charisma and presence.

Beowulf wasn't always a part of his clan's best.  He started from
nothing, much like Scyfling.  He was now going on a glorious quest of 
honor.
\section{Section 2}
\label{sec-2}
\section{Section 3}
\label{sec-3}
% Emacs 24.5.1 (Org mode 8.2.10)
\end{document}