\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[rm]{roboto}
\begin{document}
\section*{All the Notes I Ever Took in French I}
\begin{itemize}
	\item Paris is in the northern central area of France.
	\item Paris is divided into (for administrative reasons) Arrondissements.
		\begin{itemize}
			\item There are 20 of them.
			\item These are how Parisians will describe where they live in the city.
			\item The numbering is in a clockwise circling pattern starting 
				with the first one at the centre of the city.
		\end{itemize}
	\item Paris lies on the Seine river (la Seine.)
	\item The two Islands are \^{I}le de la Cit\'{e} and \^{I}le St. Louis.
	\item The Cath\'{e}drale de Notre Dame is located on the \^{I}le de la
		Cit\'{e}.
	\item Notre Dame has gargoyles.
	\item On the Seine, there are Bateau Mouches (sightseeing boats.)  During the
		winter they are closed, and during the Summer they are open.
	\item The Left Bank and Right Bank (lower and upper respectively) refer to
		the sides of the river.
	\item The left bank has the Sorbonne.  The Latin Quarter, called so because 
		Latin used to be the language of the academics.
	\item Le Louvre---
		\begin{itemize}
			\item Contains the Mona Lisa, the Venus de Milo, Winged Victory of 
				Samothrace.
			\item Louvre was once a palace of the French Kings in Paris.
			\item Tuileris was the other big palace in Paris.
			\item The pyramid is a recent (40 years old-ish) addition and is the
				modern entrance to the museum.
			\item Place de la Concorde, a big open square.
			\item Obelisk, a four-sided pillar of stone topped with a pyramid.  It was
				stolen from Egypt by Napoleon, nicknamed Cleopatra's needle.  
		\end{itemize}
	\item Place de la Concorde used to be Place de Louis XV.  Translates to place
		of peace.  Was renamed place de la revolution.
	\item Further down the Champs Elys\'{e}es is the Arc de Triomphe.
	\item H\^{o}tel de Ville is the city hall of a city.  Not a hotel.
	\item Le Centre Pompidou, named after a previous French President.  AKA 
		Beauborg.
	\item Place de la Bastille.  Bastille used to be a fortress/prison.  In 1789
		it was stormed as a symbol against the king (and as a way to get weapons.)
	\item French call Bastille Day ``La F\^{e}te Nationale.''
	\item Sacre C\oe ur is sacred heart church.  Built in the 1800s.  It sits on 
		the highest point in all Paris, at the top of Mont Martre.  Story goes that 
		Saint Denis was beheaded there, and he picked up his head afterward and
		walked a while.
	\item Moulin Rouge was a very famous caf\'e\ in the 1800s.  The name 
		translates to ``Red Windmill.''  Nowadays it's touristy and a cabaret.
\end{itemize}
\end{document}
