\documentclass[12pt]{article}
\usepackage{outlines}
\usepackage{enumitem}
\setenumerate[4]{label=\alph*.}
\setenumerate[3]{label=\roman*.}
\setenumerate[2]{label=\Alph*.}
\setenumerate[1]{label=\Roman*.}

\usepackage[margin=1in]{geometry}
\begin{document}
\begin{raggedleft}
	John Markiewicz \\
	30 March 2015 \\
	American Lit Accel. with Bucher \\
	Crucible Essay Outline \\ \\
\end{raggedleft}
\noindent
\\ PROMPT:  ``The play starts on an ominous note with Parris in a state of frenzy.  
From the very beginning the atmosphere of the play is tense and sinister.  
Nevertheless, the playwright succeeds in raising the level of tension ever 
higher throughout the four acts of the drama.  Analyze and evaluate the role of 
suspense in the play.''\\ \\
\noindent
THESIS: Suspense plays a critical role in \underline{The Crucible} in its 
role in the plot, its effects on the characters, and the way Miller uses it to 
set the mood of the play.\\
\begin{enumerate}
	\item Introduction
	\item Suspense plays a central role in the plot of \underline{The Crucible}.
		\begin{enumerate}
			\item The suspense among the people at the beginning of the play causes
				the witch hunting in the first place.
			\item The building suspense through the play dictates the direction of
				the characters' actions.
			\item There is great suspense throughout the novel surrounding the
				outcome of the trials.
		\end{enumerate}
	\item Suspense is a major influence on the characters in \underline{The 
		Crucible} and shapes their actions in several ways.
		\begin{enumerate}
			\item Suspense pushes Abigail to do horrible things to protect herself and
				sway John Proctor's actions.
			\item Suspense over the possibility of witchcraft leads to the arrest of
				figures like Rebecca Nurse by the townsfolk.
			\item Suspense is the driving force behind the actions of the townsfolk
				through the entire play.
		\end{enumerate}
	\item Suspense is one of the main aspects of the play's mood, setting the tone
		throughout the whole story.
		\begin{enumerate}
			\item The play opens to a nervous, suspenseful scene of conversation.
			\item Suspense is intense at the scene set in the Proctors' house, being
				the defining characteristic.
			\item The trial scene is very suspenseful.
				\begin{enumerate}
					\item This is further compounded by the stage direction in the scene.
				\end{enumerate}
		\end{enumerate}
	\item Conclusion
\end{enumerate}
\end{document}
