%% An outline for the college essay
%% Nothing too exciting.

\documentclass[12pt]{article}
\usepackage{outlines}
\usepackage{enumitem}
\setenumerate[1]{label=\Roman*.}
\setenumerate[2]{label=\Alph*.}
\setenumerate[3]{label=\roman*.}
\setenumerate[4]{label=\alph*.}

\usepackage[margin=1in]{geometry}

\begin{document}
\begin{raggedleft}
	John Markiewicz \\
	22 March 2015 \\
	American Lit Accel. with Bucher \\
	College Essay Outline \\
\end{raggedleft}
\noindent
\\ THESIS STATEMENT: My freshman year, a year spent at St.
	Charles, was a difficult time in my life but it helped shape
	who I am today.
\begin{outline}[enumerate]
	\1 Introduction
	\1 St Charles was an introduction to a highly structured 
		learning environment.
		\2 Prior to this, I was used to the lack of structure 
			presented by a Montessori school.
		\2 Surface elements of the High School experience were
			different, more structured, and more difficult to get
			used to.
		\2 After a while, however, I became used to the way the
			school was structured, which has aided me since.
	\1 St. Charles shaped my view of academic subjects.
		\2 Latin shaped my view of languages, even of english,
			to this day.
		\2 IPC gave me the foundation on which I've built my 
			knowledge of science since.
		\2 The level of difficulty forced me to learn time management
			and study habits, which have served me well in many ways
			since.
	\1 St. Charles changed my view of work, and how I approach
		it.
		\2 The routine  of the work taught me the value of 
			consistency.
		\2 The difficulty taught me to consider alternate solutions
			to problems, because I couldn't effectively brute-force my 
			way through things.
	\1 Conclusion
\end{outline}
\end{document}
