%%=============================================================================
%%
%%       Filename:  TSAR.tex
%%
%%    Description:  
%%
%%        Version:  1.0
%%        Created:  03/05/2015
%%       Revision:  none
%%
%%         Author:  John Markiewicz
%%   Organization:  Watterson A Cappella Choir, OSUOSC
%%      Copyright:  
%%
%%          Notes:  These notes are note-tacular.  Fear them.
%%                
%%=============================================================================
\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage[]{amsmath}
\begin{document}
\section{Background and First 3 Chapters}
\subsection{Hemingway}
\begin{itemize}
	\item Hemingway came up with the Hemingway code, summarized by the following
		ideas:
		\begin{itemize}
			\item Live Passionately
			\item Do not be controlled by others
			\item Be honest, controlled, and disciplined
			\item Take risks, be persistent
			\item Do not pity yourself, and accept death on your own terms.
		\end{itemize}
	\item Fitzgerald and Hemingway write at the same time, but there are many 
		important differences.  Like Fitzgerald, Hemingway got involved with 
		other writers.
	\item Hemingway uses a simple sentence structure and reveals fairly little.
	\item Hemingway also uses irony, sarcasm, and understatement.  So 
		Hemingway should remind me of myself in some twisted way.
	\item Hemingway was born in Oak Park, Illinois, to a doctor.  He loved the 
		woods, boxed, and played football.  Like many other writers of the 
		time (I'm looking at Fitzgerald here) he was involved in WWI.  He was 
		rejected by the US Army, as a result of eyesight.
	\item Hemingway, rather than fighting, served as an ambulance driver in 
		Italy.  Wrote \underline{A Farewell to Arms} about it.  
	\item In Paris, he met other writers including Ezra Pound, Gertrude Stein, 
		and F. Scott Fitzgerald.
	\item These American authors living in Paris were called ``expatriates,'' 
		and Stein named the generation of writers ``The Lost Generation.'' 
		Stein had an influence on Hemingway, advising his style and telling 
		him to concentrate more.
	\item In 1923, Hemingway saw his first bullfight in Pamplona, Spain.  He 
		used his experiences with bullfighting in writing \underline{The Sun
		Also Rises.}
	\item Published TSAR in 1926, and it was a critical success.
	\item Also wrote \underline{Farewell to Arms}, \underline{For Whom the 
		Bell Tolls}, and \underline{The Old Man and the Sea}.
	\item Received the Nobel Prize for literature.
	\item Uses the quote from Stein, and a quote from Ecclesiastes
\end{itemize}
\subsection{Backdrop of the Book}
\begin{itemize}
	\item Jake Barnes, our narrator, is a WWI vet in the newspaper business.  
		He was injured in the war.
	\item Robert Cohn is a Jewish man from a wealthy family, and is apparently 
		a mediocre writer (assuming we can trust our narrator.)
	\item Lady Brett Ashley is Jake's love aged 34.  She plans on getting a 
		divorce from Lord Ashley.
	\item Bill Gorton is Jake's friend met in Spain and a writer.
	\item We find Cohn has little self-confidence and is controlled to a fair 
		extent by the women in his life.
	\item Cohn has been discriminated against for being Jewish, and while he 
		hates boxing he hides behind it and uses it to feel safer.
	\item Cohn was from one of the richest and oldest Jewish families in New 
		York.  Robert was nice, friendly, but shy.  It made him bitter.
	\item Braddocks is Cohn's literary friend, and Barnes is his literary 
		friend.  Cohn wrote a novel, but it was a critical failure.
\end{itemize}
\subsection{Chapter 1 through Chapter 3}
\begin{itemize}
	\item Cohn had been reading \underline{The Purple Land} and is taking it 
		too literally.  Jake thinks Cohn needs to look more realistically at 
		life.  Cohn needs to live life rather than having all these Romantic 
		delusions.  Jake believes that nobody ever lives life to the fullest 
		except for bullfighters.  Robert is not so interested in bullfighters, 
		and Jake says he should read a book about it.
	\item Robert wants to see a different life than he has, Jake is satisfied 
		with what he's doing.  Jake has tried going to other countries, and 
		says ``You can't get away from yourself by moving.  I've tried all 
		that.''  This is the idea you can't run away from death or yourself.
	\item We are introduced to Lady Brett Ashley, and she was ``Damned good 
		looking.''  She wears her hair in the style of the 20s, short and 
		brushed back ``Like a boy's.''
	\item There is evidence she and Jake are more than just casual friends.  
		She dodges Robert's attempts at flirtation.  At her entrance Jake 
		immediately points out her presence, and is insulted that he brought 
		Georgette.  She calls him darling.
	\item Ends the chapter saying she is miserable.  She acts carefree, but
		is unhappy with the circumstances.
\end{itemize}
\section{Chapters 4-6}
\subsection{Chapter 4}
\begin{itemize}
	\item Brett is unreliable, and portrayed as not knowing what she wants and 
		speaks differently from how she acts.  
	\item Brett is assertive and independent, but ``afraid of so many 
		things.''  Jake claims he can see through her exterior.
	\item ``Don't we pay for all the things we do?'' -Jake
	\item ``When I think of the hell I've put chaps through, I'm paying for it 
		all.''  -Brett
	\item In response to this, Jake says his war injury is supposed to be 
		funny, and that he never thinks of it.
	\item Jake has grown tired of the subject, though ``Certain injuries are a 
		source of merriment'' but are a pain for those with them.
\end{itemize}
\subsection{Chapter 5}
\begin{itemize}
	\item Zizi and Mippipopolous.  Mippi knows a lot about people, and owns a 
		chain of sweet shops.  Brett says he's ``one of us.'' This suggests he 
		is aristocratic, from America and living in Europe, frivolous, and all 
		the like things.
	\item Jake takes this walk through the city streets, walking past cafes.  
		Comes to a statue of Marshall May, a French military hero known for
		his bravery.
	\item Jake has a very important relationship with bullfighting, he takes 
		in bullfighting papers or something.  He mentions how the Catholic 
		Church says he shouldn't think about his permanent injury.
	\item Jake lays awake thinking about Brett, and cries.  He wants to be 
		with her, but feels there is no chance.  They go out again, and kiss, 
		and he goes back upstairs, gets into bed, and says ``it is awfully 
		easy to be hard-boiled in the daytime, but at night is another thing.''
	\item He throws out the idea that Brett isn't even worth crying about.
\end{itemize}
\subsection{Chapter 6}
\begin{itemize}
	\item Jake has a conversation with a couple other newsmen, at a press 
		conference.  Jake does not consider these men friends, just 
		acquaintences.  They don't know each other very well.  The other 
		newsmen are married and have kids.
	\item Cohn has an incapacity to enjoy Paris.  Jake thinks he got this from 
		the writer H.L. Mencken.  He implies this is where Robert gets many of 
		his ideas. 
	\item Jake encounters Harvey Stone, and they see Robert Cohn coming and 
		Harvey is kind of a dick.  Says Cohn is an unintelligent moron.  Then 
		later says he is a case of arrested development.
	\item Cohn takes this pretty well, but threatens Stone a bit.  Jake notes 
		he feels he has not shown Robert clearly.  Up until Cohn fell in love 
		with Brett, he had never made a remark that would detatch him from 
		others.  Externally, he had been formed at Princeton but internally he 
		had been formed by women in his life.
	\item Francis is upset that Robert refuses to marry her.  Jake dislikes 
		how Robert allows Francis to walk all over him.
	\end{itemize}
\section{Chapter 7-9}
\subsection{Chapter 7}
\begin{itemize}
	\item Brett pays Jake's concierge, and in Jake's room show up Brett and 
		the Count.
	\item The count is a perfect example of a member of the lost generation, 
		and he's all about satisfying physical desires.  He only smokes good 
		cigars, only drinks champagne out of a magnum, etc.
	\item He's been through multiple wars and revolutions.  He's also drowning 
		in women when Brett and Jake leave.
	\item He's ``BIG.  He's FAT.  He's LARGE,'' --Bucher 2015
	\item They talk of titles, and the count talks of how a title is a bother.  
		Brett says they're useful, but Mippi says they're more trouble than 
		they're worth.
	\item Jake not having a title is indicative of his different-ness.  The 
		count says to Brett that she's always drinking, which is a result of 
		wanting to avoid serious conversation.
	\item Count says because he has lived so much, he can enjoy so much, and 
		because he has come to know all the values he is successful.  Brett 
		says he hasn't any values, and that he's dead.  She's just the same.
	\item Count is compared to Jake throughout the chapter.  They have 
		different views of danger, and the Count tries not to be alone ever.
	\item Jake actually fought in a war, the count pretends he was in a war.
	\item Jake values nature, his job, things that aren't wealth or image.
	\item In response to the idea Jake and  Brett ought be married, Jake says 
		``We ought to lead our own lives.''  This is all lost generation-y.
	\item They continue on to a club, and Brett brings up Michael.  She says 
		she's going to marry him, and hasn't thought about him for a week, and 
		this will be her third marriage.
	\item She again says she is so miserable.  Jake says she has made no 
		progress, and that he's going through something that has happened 
		before.
	\item Brett is shown here to be fairly incapable of finding love and 
		fulfillment, and is miserable.
	\item The count supports Zizi, and that he has a future, but the Count 
		doesn't want him around.
	\end{itemize}
\subsection{Chapter 8}
\begin{itemize}
	\item Jake is pleased to have time with nothing to do with Cohn or Brett.
	\item Robert got into boxing as a method of coping, but this is not the 
		reason the Black Boxer got into it.
	\item Gorton brings up the stuffed dogs, which some critics say are 
		symbolic of people trying to adjust to life after the war, as they are 
		only imitating life.
	\item Brett is indecisive, and doesn't know how she feels, but Jake knows 
		what he wants and isn't fake.  He just can't get it.
	\item Brett makes it clear that she likes Paris, and regrets leaving.
	\item Gorton drinks, a lot, and views being undaunted as pretty important.
	\item Jake makes his point about Paris, saying it's crowded with Americans.
		Especially Americans who want the quaint, untouched ideal of Paris, and
		he has a disdain for the Americans who do this.
	\item They circle the island, and it's quite dark.  Jake has an affinity
		for nature, which is shown in this walk along the river.  This is in
		some sense the first time he has been satisfied with Paris, and he 
		is enjoying the night.
	\item This is one of the rare points where Paris hasn't been spoiled by the
		presence of his compatriots.
	\item Toward the end of the chapter, we meet Brett and Michael.  Michael,
		like Brett, is morally bankrupt with the benefit of also being
		financially bankrupt.
	\end{itemize}
\subsection{Chapter 9}
\begin{itemize}
	\item This chapter has Jake angry with Robert, and there is definitely a 
		breach in their friendship (if at any point one could have called it
		that.)  There is animosity and disgust.
	\item Chapter opens, Jake receives a letter from Robert.  In the morning,
		when he writes Robert back, that they would leave on the 25th unless
		they decided otherwise.
	\item Brett asks if Robert will be on the trip, and asks if it'll be hard
		on him.  You can tell Jake is unhappy, and sarcastic and blunt with her.
		This is in no small part because she is rubbing it in his face.
	\item Jake being so sarcastic shows an aspect of himself that isn't often
		seen through the rest of the novel.
	\item Jake is volunteering to be with Brett and Michael, showing remarkable
		similarities to Nick ``Third Wheelin{'}'' Carraway
	\item The behavior of the conductor is indicative of money neither being
		power nor influence, and possibly that money is not satisfying.  
	\item People are off pretending to be Catholic, and those who aren't 
		doing so aren't getting to eat but are enjoying themselves and nature
		more.  This is nature versus hurrying to satisfy one's needs.
	\item Jake, who's actually Catholic, is kind of offended by those who are
		pretending to be Catholic.
	\item They all are constantly moving, even possibly at random, and are all
		trying to escape themselves.  This is symbolic.
	\item Bill has anger toward Robert, and it's partially driven by Robert's
		hatred of Jews.  He's angry both about Robert's superiority and his
		Jewishness.
	\end{itemize}
\section{Chapter 10-18}
\subsection{Chapter 10}
\begin{itemize}
	\item This chapter contains a lot of religious references, and mention of
		Jake's Catholicism.
	\item Jake goes to the Cathedral, pray for others, himself, money (which
		reminds him of the count,) which ends up bringing him onto a tangent.
	\item Jake regrets being a rotten Catholic, and views Catholicism as a grand
		religion and only wishes he could be a better Catholic.
	\item Cohn is nervous, as he is unsure if Jake knows about Cohn and Brett.
		Jake says he will go to the station with Cohn, just to devil him (and 
		make him more nervous.)  Jake is pretty spiteful here.
	\item Jake enjoys this nervousness, and says Cohn has a tendency to bring
		out the worst in people.
\end{itemize}
\subsection{Chapter 15}
\begin{itemize}
	\item This is pre-bullfight.  Robert says he is only worried he'd be bored,
		an indication of his lack of understanding of bullfighting and being out
		of his element.
	\item Cohn has typically been a participant in sports, not a spectator.
	\item Brett worries if she'll be able to go through with it alright.  Bill
		says to Cohn that he isn't likely to be too bored.
	\item Robert has decided to live life and fall in love outside his value
		system, and it shows.
	\item Pedro Romero was 19, alone, and handsome.  
	\item Robert is sickened by the bullfight, Brett doesn't mind, and Brett
		is into Pedro Romero.
	\item Romero is a good bullfighter, knowing how to control the bull without
		wasting its energy, working it so it is tired at the end.  He works close
		to the bull, without using any trick.  He is calm and skillful, and has
		grace and purity of movement.
	\item Romero is a contrast to Robert and relates to everyone's values and
		all that.
\end{itemize}
\subsection{Chapter 16}
\begin{itemize}
	\item Montoya wants to protect Romero from the corruption of Americans and
		foreigners in general, tells Jake not to give Romero the message from the
		ambassador.
	\item Jake says to pretend like he forgot to give it to him.  Jake sees the 
		importance of not spoiling Romero, then does a face-heel turn in the 
		situation with Brett.
	\item Montoya shows up and is disappointed.  Good work, Jake.
	\item Brett is into the Romero, and they all drink to him.  Jake keeps
		interrupting, Brett tells Mike to shut up.  Mike asks Cohn if he thinks
		he belongs among them, and in contrast to Romero Mike recognizes that 
		Robert is a loser.
	\item Cohn sat at the table, looking insulted but seemingly enjoying it.
	\item Cohn prepares to fight.  He's trying to be assertive and dominant.  
		This is not at all in his nature.
	\item Jake hates him.  Brett also hates him, his ``Damned Suffering.'' 
	\item Brett asks if Jake loves her, and then immediately says she's fallen
		for Romero.
	\item ``I've lost my self-respect.'' -Brett
	\item Cohn loses it, and beats the hell out of a few people.  
	\item Cohn calls Jake a damned pimp (and hell yeah he is) and then proceeds
		to punch him.
	\item Jake is bothered by the word pimp, apparently.
	\item When Jake returns to the hotel, he wants a bath.  The water won't
		run.  
	\item Life is uncertain, and death may come at any time.  The story of the
		young man killed in the running of the bulls is an example.
	\item Cohn had all these ideas of what should happen and true love and all 
		that.  This is dumb.
	\item Cohn is a dick, and Romero ``Ruins'' Cohn, making it so he won't ever
		knock people about again.
	\item Romero's continued force against Cohn makes Romero the better man and
		ruins Cohn's view of his chance at love.  
	\item Brett is very sarcastic about her experiences with the British
		aristocracy.  
\end{itemize}
\subsection{Chapter 18}
\begin{itemize}
	\item It is the last day of the fiesta, and Mike starts in on Brett.  She
		gets irritated, and starts talking about Romero.  Romero's people are very
		angry about her.
	\item Brett wants to pray, but it isn't very successful.  She gets nervous
		in Church, and has a bad face for Church.
	\item She looks like the ``sinful women'' of the 1920s, which was in contrast
		to the Church's morality.  By her looks, once can tell she isn't a moral
		person and she recognizes this.
	\item She says she's never gotten anything she's prayed for.  Jake says he's
		very religious, which is only kind of true.
	\item Jake says he sees her as different now, she is in love and has changed.
		She even says so herself.
	\item She doesn't want to be stared at anymore.
	\item Distinction is drawn between the bullfighters.
	\item ``In bullfighting, they refer to the terrain of the bull, and the
		terrain of the bullfighter.'' When a bullfighter works close to the bull,
		he is in great danger and close to the bull.  Belmont always works in the 
		terrain of the bull.
	\item Belmont is kind of washed-up; the public were against Belmont and were
		therefore for Romero.
	\item Belmont's return from retirement had been spoiled by Romero, who was a
		very good bullfighter.  Pedro Romero had the greatness, a love of
		bullfighting and of the bulls.  All things were controlled in the fight by 
		Romero.
	\item The distinction is drawn between brilliant bullfighting and perfect 
		bullfighting.
	\item Romero is through bullfighting cleaning himself of the fight with Cohn.
	\item As the sun sets for Belmont, the Sun Also Rises for Romero.
	\item Romero gives Brett a bull ear, and they all go over to the cafe.
	\item Jake asks Bill where Edna is, he doesn't know, and they begin to talk
		about Robert.  Jake assumes Robert will take back up with Francis.
	\item Jake is very drunk, drunker than he ever had been.  This doesn't really
		help his conscience any.
	\item Thus ends book 2.
\end{itemize}
\section{Book 3}
\begin{itemize}
	\item Mike is completely bankrupt in many ways, and it is suggested that his
		lack of values has created for him a great void.
	\item Jake is trying to escape the clamor of the fiesta, and decides to go
		to San Sebastian.
	\item They have lunch, and Jake points out that Montoya didn't come near them.
	\item Jake symbolically rubs the rod case with dust, as the last thing
		connecting him to Spain and the Fiesta.  He says he is through with fiestas
		for a while.
	\item Jake has dinner, overtips the waiter to distinguish himself.
\end{itemize}
\end{document}
