\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{fullpage}

\begin{document}
\section{New Content}
\subsection{Monday, 13th April}
\begin{enumerate}
	\item Slope Fields are drawings with the slope at any given point, and can 
		tell a lot about a differential equation without solving it.
	\item A big reason slope fields are useful is that there are some differential
		equations we are unable to solve.  The handout has some examples and rules.
	\item Drawing out a slope field by hand is tedious and unpleasant, so don't
		do it unless you have to.
\end{enumerate}
\subsection{Tuesday, 14th April}
\begin{enumerate}
	\item Continuing from April Fools' Day:
		\begin{align}
			\setcounter{equation}{0}
			\frac{dy}{dx} &= 4xy \\
			\int_{}^{}\frac{1}{y}dy &= \int_{}^{}4xdx \\
			\ln y &= 2x^2+C_1 \\
			y &= Ce^{2x^2}
		\end{align}
	\item $\frac{dy}{dt}$ is the same as a rate of change, but it's also a part
		of a differential equation.
		\begin{align}
			\setcounter{equation}{0}
			\frac{dy}{dt} &= ky \\
			\int \frac{1}{y}dy &= kdt \\
			ln y &= kt+c \\
			y &= Ce^{kt}
		\end{align}
	\item {\bf Growth and Decay} gives us the equation $y = Ce^{kt}$ where 
		$C$ is the initial value, $k$ is the constant of proportionality, $e$ is
		$e$, and $t$ is time.  If $k$ is positive, it is growing, and if negative,
		it is decaying.
	\item In many problems using growth and decay, we want to first find k.
		\begin{align}
			\setcounter{equation}{0}
			4 &= Ce^{2k}\\
			4 &= 2e^{2k}\\
			2 &= e^{2k} \\
			\ln 2 &= \ln e^{2k} \\
			\frac{1}{2} \ln 2 &= k
		\end{align}
	\item Continuing on, using this fact:
		\begin{align}
			y &= 2e^{\frac{t}{2}\ln 2}\\
				&= e^{\ln 2^{\frac{t}{2}}} \\
				&= 2(2^{\frac{t}{2}} \\
				&= 2(2^{\frac{3}{2}})
		\end{align}
	\item This sort of thing can be applied as well to half-lives.
		\begin{align}
			\setcounter{equation}{0}
			y &= Ce^{24100k} \\
			\frac{y}{c} &= e^{24100k} \\
			\ln \frac{1}{2} &= 24100k \\
			k &= \frac{\ln \frac{1}{2}}{24100}
		\end{align}
		if $k$ is half-life, then $k=\frac{ln\frac{1}{2}}{h}$ and if k is a
		constant of proportionality then h is $\frac{ln\frac{1}{2}}{k}$.
\end{enumerate}

\section{AP Preparations}
\subsection{Monday, 20th April}
\begin{enumerate}
	\item[3. ] From the 2000 AP Exam
		\begin{enumerate}
			\item $x = -1$ is a relative minimum because $f\prime$ goes
				from negative to positive.
			\item $x = -5$ is a relative maximum because $f\prime$ goes
				from positive to negative.
			\item $(-7, -3) \quad (2, 3) \quad (3, 5)$
			\item For this we check the maxima and endpoints.  $x = 7$
				and $x = -7$ are endpoints.  It is $x = 7$ since it's 
				the best.
		\end{enumerate}
\end{enumerate}

\subsection{Wednesday, 22nd April}
\begin{enumerate}
	\item From the board at the time:
		\begin{align}
			\setcounter{equation}{0}
			E(t) &= \frac{15600}{(t^3-24t+160)} \\
			L(t) &= \frac{9890}{t^2-38t+370}
		\end{align}
\end{enumerate}
\subsection{Wednesday, 29th April}
\begin{enumerate}
	\item $ \lim{x \to 1^-} = e$
	\item $\lim x \to 1^+ = 0$
	\item The limit does not exist.
	\item \begin{align*}
			x^2 &= kx + 1\\
			1 &= k + 1\\
			0 &= k
		\end{align*}
	\item \(\frac{1}{10}\)
	\item \(\frac{2}{\pi}\)
	\item 2
	\item Basically just more L'hopital's review.
	\item \begin{align}
			\setcounter{equation}{0}
			\text{Given Rate:  }\frac{dy}{dt} &= -2\\
			\text{find }\frac{dx}{dt}\text{ when }x &= \frac{-3}{2}
		\end{align}
	\item \begin{align}
			\setcounter{equation}{0}
			k(t) &= (t^2-9)^{4/5}\\
			y &= u^{4/5} \qquad u = t^2 - 9\\
			y^{\prime} &= \frac{4}{5} u^{4/5}\\
		\end{align}
\end{enumerate}

\subsection{Friday, 1 May}
The AP test is soon.  Be afraid.
\begin{enumerate}
	\item \begin{align}
			\setcounter{equation}{0}
			h(x) &= x^2 arcsec x\\
			h'(x) &= x^2\left(\frac{1}{x\sqrt{x^2-1}}\right)\\
								 &= \frac{x}{\sqrt{x^2-1}}+2xarcsec(x)
		\end{align}
	\item \begin{align}
			\setcounter{equation}{0}
			y &= \ln (x^2+4) - \frac{1}{2}arctan\frac{x}{2}\\
			y' &= \frac{2x}{x^2+4} - \frac{1}{2} \times \frac{\frac{1}{2}}
				{\frac{x^2}{4}+1} \\
		\end{align}
		Solve from here for practice, since O'connor did the favor of erasing it
		for us.
	\item Rolle's theorem explains that where the derivative of both endpoints 
		is the same the second derivative has to be 0 at some point in the thing.
	\item Mean value theorem is the broader variation on Rolle's theorem.  Both
		assume it is differentiable (and thus continuous as a requirement, as a
		function is differentiable iff it is continuous.)
\end{enumerate}
\end{document}
